Hydra Battles and Cie

### 2021-05-17 doc/part-hydras.tex
minor changes

\begin{remark}
Some notations (mainly names of fast-growing functions) of our development may differ slightly from the litterature. Although this fact does not affect our proofs, we are preparing a future 
version where the names $F\_alpha$, $f\_alpha$, $H\_alpha$, etc., are fully consistent with the cited articles. This change will be provisionally made in a branch \texttt{Hardy} (in reference to the Hardy hierarchy).
\end{remark}
%\section{Introduction}

@@

\begin{remark}
The upper bound of the considered interval has been chosen to be  $l-1$ and not $l$, in order to simplify some statements and proofs in composition lemmas associated with the ordinals of the form $\alpha\times i$ and 
$\omega^\alpha\times i + \beta$.
In order to consider any ordinal below $\epsilon_0$, we consider a special case for $\alpha=0$.
\end{remark}

@@

It is worth looking at the answer from \texttt{Equations} and check (with \texttt{About} ) all the lemmas this plug-in gives you for free. We show here only a part of \coq's anwer.

@@

\label{sect:hardy}
In order to give a feeling on  the complexity of the functions  $L_\alpha$s, we compare them with a better known family of functions, the so called \emph{Wainer-Hardy hierarchy} of fast growing functions,
presented for instance in~\cite{Promel2013}. 
\index{maths}{Rapidly growing functions!Hardy Hierarchy}

>>>>

\begin{remark}
Some notations (mainly names of fast-growing functions) of our development may differ slightly from the litterature. Although this fact does not affect our proofs, we are preparing a future 
version where the names $F\_alpha$, $f\_alpha$, $H\_alpha$, etc., are fully consistent with the cited articles. This change will be provisionally made in a branch called \texttt{Hardy} (in reference to the Hardy hierarchy).
\end{remark}
%\section{Introduction}

@@

\begin{remark}
In~\cite{KS81} Ketonen and Solovay consider the least natural number $l$ where the interval $[k,l]$ ($l$ included) is $\alpha$-large, and call $H_\alpha$ the function which maps $k$ to $l$. We chose to consider intervals $[l,k)$ instead of $[l,k]$
in order to simplify  some statements and proofs in composition lemmas associated with the ordinals of the form $\alpha\times i$ and 
$\omega^\alpha\times i + \beta$.
Clearly, both approachs are related through the equality
$L_\alpha(k)=H_\alpha(k)+1$, for any non-null $\alpha$ and $k$.
\end{remark}

@@

It is worth looking at the answer from \texttt{Equations} and at all the lemmas this plug-in gives you for free. We show here only a part of \coq's anwer.

@@

\label{sect:hardy}

\begin{remark}
  Indeed, the functions presented in this section are a \emph{variant} of the Hardy hierarchy of functions. In the future versions of this development, we will correct the references to the litterature.
\end{remark}

In order to give a feeling on  the complexity of the functions  $L_\alpha$s, we compare them with a better known family of functions, the so called \emph{Wainer-Hardy hierarchy} of fast growing functions,
presented for instance in~\cite{Promel2013}. 
\index{maths}{Rapidly growing functions!Hardy Hierarchy}
